---
title: "Carbon Lock-in task CD LINKS"
author: "Aman Malik and Chirstoph Bertram"
date:   "15 October 2018"  
output: 
html_document:
  toc: "true"
  toc_depth: "2"
---

```{r global settings, include=FALSE}
# setting global settings for knitr
# echo=TRUE/FALSE whether to include R source code in the output file
# knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path = "figure-carbonlockin/",cache = T,echo=F)
```

```{r}
#### Some comments on knitr arguments ########
#warnings=FALSE, switches off all warnings from the trunk
#eval = FALSE, doesn't evaluate the chunk. Useful for packages that are not yet open-source, e.g., moinput
# include=FALSE, suppresses messages associated with loading packages
```

```{r req packages,message=FALSE, warning=FALSE, include=FALSE,results='hide'}
# library(quitte)
# library(moinput)
library(tidyverse)
library(reshape)
library(data.table)
```

```{r all_data,include=FALSE,eval=FALSE,message=FALSE,purl=FALSE}

#read in data
all <- invisible(fread("cdlinks_compare_20180508-032045.csv",header=TRUE)) #seems to be missing the V3 variants
all <- invisible(fread("cdlinks_compare_20180810-010937.csv",header=TRUE)) #only MESSAGE
all <- invisible(fread("cdlinks_compare_20180720-122848.csv",header=TRUE)) #only MESSAGE, AIM/CGE, IMAGE3.0, POLES, WITCH
all <- fread(input = "cdlinks_compare_20180615-153808.csv",header = T, sep = ',') #all V3 and V4 scens

#filter for desired set of time series
models <- unique(all$MODEL)
regions <- "IND" # unique(all$REGION)
scens <- unique(all$SCENARIO)
# How were these variables selected?
variables <- as.character(read.csv2("plotstyles_CLI.csv")$name)

all  <- all[all$MODEL %in% models & all$SCENARIO %in% scens & all$REGION %in% regions & all$VARIABLE %in% variables,]

all <- invisible(melt(all,measure.vars=names(all)[grep("[0-9]+",names(all))],variable.name = "period",variable.factor=FALSE))

all$period <- as.numeric(all$period)
all <- all[!period %in% c(1950,1955,1960,1965,1970,1975,1980,1985,1990,1995,2000,2001,2002,2003,2004,2006,2007,2008,2009,2011,2012,2013,2014,2016,2017,2018,2019,2021,2022,2023,2024,2026,2027,2028,2029,2031,2032,2033,2034,2036,2037,2038,2039,2041,2042,2043,2044,2046,2047,2048,2049,2051,2052,2053,2054,2056,2057,2058,2059,2061,2062,2063,2064,2066,2067,2068,2069,2071,2072,2073,2074,2076,2077,2078,2079,2081,2082,2083,2084,2086,2087,2088,2089,2091,2092,2093,2094,2096,2097,2098,2099,2101,2102,2103,2104,2106,2107,2108,2109)]
# Rename columns
setnames(all, "MODEL", "model")
setnames(all, "SCENARIO", "scenario")
setnames(all, "REGION", "region")
setnames(all, "VARIABLE", "variable")
setnames(all, "UNIT", "unit")

all  <- na.omit(all) # remove rows containing NAs

#make variables a factor, so that the order in facets can be manipulated easily
all$variable <- factor(all$variable)

all$model1 <- all$model
all$scenario1 <- all$scenario
all <- unite(all,col="modscen",c("model1","scenario1"),sep = " - ")
#make variables a factor, so that the order in facets can be manipulated easily
all$model <- factor(all$model)
all$scenario <- factor(all$scenario)
all$modscen <- factor(all$modscen)

#get rid of scenarios not interesting for us
scens_other <- c(grep("rec",unique(all$scenario),value=T),
                  grep("USD",unique(all$scenario),value=T),
              grep("Food",unique(all$scenario),value=T))
all <- all[!scenario %in% scens_other]

#get rid of V3 variants for models that have V4
v3scens <- grep("_V3",unique(all$scenario),value=T)
v4scens <- grep("_V4",unique(all$scenario),value=T)
v4mods <- unique(all[scenario %in% v4scens]$model)
all <- rbind(all[!model %in% v4mods],all[model %in% v4mods & scenario %in% v4scens])

all <- all %>% 
  mutate(model_scope=ifelse(model=="India MARKAL"|model=="AIM/Enduse 3.0","national","global"))
# Early scenario
early <- all[all$scenario %in% c("NPi2020_1000_V4","NPi2020_1000_V3","NPi2020_low_V3"),]
early <- add_column(early,scen_name = "Early action")
# Delay scenario
delay   <- all[all$scenario %in% c("INDC2030i_1000_V4","INDC2030i_1000_V3","INDC2030_low_V3"),]
delay <-  add_column(delay,scen_name = "Delayed action")
whole <- rbind(early,delay)
fwrite(whole,"")
save(whole,file="data_IND.RData")
```
```{r}
load("data_IND.RData")
```


```{r historical data,include=FALSE,eval=FALSE}
# Relevant historical and bottom-up data 
# historical IEA data (PE, SE, FE,Trade), and CEDS emissions data
setConfig(forcecache = TRUE)
historical <- calcOutput("Historical",aggregate = F)# aggregate = T not working at the moment, use when available
historical <- collapseNames(historical,collapsedim = 1)
hist_IEA_CEDS <- as.data.frame(historical) 
hist_IEA_CEDS <- hist_IEA_CEDS[,-1]
# Format "Region"   "Year"  "Source"   "Variable" "Value"
names(hist_IEA_CEDS)[c(3,4)] <- c("Source","Variable")
# historical Renewable Energy Capacity data 
hist_IRENA_cap <- as.data.frame(calcOutput("Capacity",aggregate = T))
hist_IRENA_cap <- hist_IRENA_cap[,-1]
hist_IRENA_cap$Source <- "IRENA"
hist_IRENA_cap <- hist_IRENA_cap[,c(1,2,5,3,4)]
names(hist_IRENA_cap) <- names(hist_IEA_CEDS)

# nuclear bottom-up data
nuclear_IAEA <- as.data.frame(calcOutput("CapacityNuclear",aggregate = T))
nuclear_IAEA <- nuclear_IAEA[,-1]
nuclear_IAEA$Source <- "IEA"
nuclear_IAEA <- nuclear_IAEA[,c(1,2,5,3,4)]
names(nuclear_IAEA) <- names(hist_IEA_CEDS)
# coal plants bottom up data
coal_EndCoal <- as.data.frame(readSource("EndCoal"))
coal_EndCoal <- coal_EndCoal[,-1]
coal_EndCoal$Year <- "2018"
coal_EndCoal$Source <- "EndCoal"
coal_EndCoal <- coal_EndCoal[,c(1,2,5,3,4)]
names(coal_EndCoal) <- names(hist_IEA_CEDS)
# coal_EndCoal$Value <- as.character(coal_EndCoal$Value)
# IEA_WEO 2016 investment costs
capacity_costs_IEA <- as.data.frame(calcOutput("DiffInvestCosts",aggregate = T))
capacity_costs_IEA <- capacity_costs_IEA[,-1]
capacity_costs_IEA$Source <- "IEA_WEO"
capacity_costs_IEA <- capacity_costs_IEA[,c(1,2,5,3,4)]
names(capacity_costs_IEA) <- names(hist_IEA_CEDS)

# bringing all historical and bottom up data together; format- region, Variable Name, Year, Value
hist_and_botmup <- rbind(hist_IEA_CEDS,hist_IRENA_cap,nuclear_IAEA,capacity_costs_IEA,coal_EndCoal)   


# historical nuclear 
save(hist_and_botmup,file="HistandBotmup.RData")
```

```{r}
load("HistandBotmup.RData")
```
### Objective
The objective of the current task is to analyse and compare the structure of the Indian power sector under various mitigation regimes. It is often said that models are as good as the assumptions they are based on. Through this analysis, we hope to comment upon the plausibility of the assumptions used by these models. 

### Methodology

 Global Integrated Assessment Models (IAMs) informed national energy-economy models and national IAMs in terms of national emission budgets consistent with long-term climate targets. National models often focus on nation-specific development issues, and have a stronger grasp on technologies and policies.  

#### Explanation of scenario names

| Scenario name |  National Models | Global Models  |
|---------------|------------------|----------------|
|Early action|Cumulative national emissions (budget/target) from 2011-2050, climate policy starts in 2020|Cumulative global emissions target of 1000GtC, climate policy starts in 2020|
|Delayed action|Cumulative national emissions (budget/target) from 2011-2050, climate policy starts in 2030|Cumulative global emissions target of 1000GtC, climate policy starts in 2030|

```{r generic plot functions}
# Writing a generic function for a line-type ggplot
line_type_1 <- function(data_s,hist_s,years){
  ggplot()+
  geom_line(data = data_s , aes(x=period,y=value,group=interaction(model,scen_name),linetype=scen_name,color=model_scope)) +
   labs(
    x = "Year" ,
    y = paste(data_s$variable,"(",data_s$unit,")"),
    color = "Model Scope",
    linetype = "Scenario Type"
  ) +
  theme_bw()+ 
  coord_cartesian(xlim = c(2005,2050),ylim =c(1.3*min(data_s$value[data_s$period<2050]),1.3*max(data_s$value[data_s$period<2050])))+
  annotate(geom = "point",x = years,y=hist_s$Value)
  # ggsave(file=paste(gsub(c("\\||\\/"),"_",unique(data_s$variable)),"_1",".png",sep=""))
}

line_type_2 <- function(data_s,hist_s,years){
  ggplot()+
  geom_line(data = data_s %>% filter(model %in% c("India MARKAL","AIM/Enduse 3.0")), aes(x=period,y=value,group=interaction(model,scen_name),linetype=scen_name,alpha=model)) +
geom_line(data = data_s %>% filter(!model %in% c("India MARKAL","AIM/Enduse 3.0")), aes(x=period,y=value,group=interaction(model,scen_name),color=model,linetype=scen_name))+
    labs(
    x = "Year" ,
    y = paste(data_s$variable,"(",data_s$unit,")"),
    color = "Global Model",
    alpha="National Model",
    linetype = "Scenario Type")+
  theme_bw()+ 
  coord_cartesian(xlim = c(2005,2050),ylim =c(1.3*min(data_s$value[data_s$period<2050]),1.3*max(data_s$value[data_s$period<2050])))+
  scale_colour_brewer(palette = "Set1")+
  scale_alpha_discrete(range = c(0.95, 0.65))+
  annotate(geom = "point",x = years,y=hist_s$Value)
  # ggsave(file=paste(gsub(c("\\||\\/"),"_",unique(data_s$variable)),"_2",".png",sep=""))
  }

```
### Results and Discussion

#### CO2 Emissions- Total and Electricity sector
```{r co2 emissions,fig.show='hold',out.width="50%",warning=FALSE}

whole_emi <- whole[whole$variable=="Emissions|CO2",]

# historical emissions //India// Fossil Fuel and Industry
hist_emi <- hist_and_botmup %>% filter(Region=="IND", Year %in% c(2005,2010),Variable =="Emi|CO2|Energy (Mt CO2/yr)") 

# geom_line(data = data_s , aes(x=period,y=value,group=interaction(model,scen_name),linetype=scen_name,color=model_scope))
# ggplot()+geom_polygon(data=whole_emi %>% filter(period<2050),aes(x=period,y=value,group=interaction(model,scen_name)))
#### Emissions from the Electricity sector
#plot emissions electricity sector 

whole_emi_elec <- whole[whole$variable=="Emissions|CO2|Energy|Supply|Electricity",]
# historical emissions //India// Fossil Fuel and Industry
hist_emi_elec <- hist_and_botmup %>% filter(Region=="IND", Year %in% c(2005,2010),Variable =="Emi|CO2|Energy|Supply|Electricity (Mt CO2/yr)") 
# share is the share of electricity emissions to total emissions

line_type_1(whole_emi,hist_emi,c(2005,2010))
line_type_2(whole_emi,hist_emi,c(2005,2010))
line_type_1(whole_emi_elec,hist_emi_elec,c(2005,2010))
line_type_2(whole_emi_elec,hist_emi_elec,c(2005,2010))
```
The top two figure show the total CO2 emissions for India, including the landuse sector. The figure on the top left shows the two national models in blue and the 9 global models in red. The top right figure shows the same data but now also with the names of the models. The continuous lines show delayed action, i.e., climate mitigation starts in 2030 (before only NDCs), while early action scenarios, in dashed lines represent current policies in 2020 followed by cliamte mitigation. _Climate mitigation_ means that from that year on, the model needs to comply by a carbon budget which is achieved by having a carbon price.  From these two figures, it is clear that both national models have no clear peaking year; in fact one model shows no peak in emissions but only a slight decrease in the growth of emissions. Most global model, on the other hand, show a peak year, which is either 2020 or 2030 depending upon a scenario. There is a considerable spread of emissions in both national and global models. National model emissions are higher than the global model emissions due to a higher carbon budget. The two black dots are only sector historical emissions; which represent xx% of the total emissions of India. Most models, get this number right.

The bottom two figures show the share of emissions generated from electricity combustion. Here the inteesting finding is that although national models have no peak in total emissions, they agree with global models that electricity emissions need to peak. Unlike global models which immediately fast track on steep electricity sector decarbonisation after 2020 (in early action), or 2030 (in delayed action), most reaching zero or close to zero (with some even negative) emissions in 2050, the national models cut emissions but not drastically. We will later see, what is the structure of the power mix in 2050, and what is contributing these emissions: is there a shift from coal to gas?, from coal w/o CCS to coal with CCS. Comparing from historical numbers, almost all except one outlier seem to get the electricity emissions correct.


#### Share of emissions - Electricity sector and coal power plants
```{r,warning=FALSE,fig.show='hold',out.width="50%"}
# Share of Electricity to total CO2 Emissions
whole_emi_elec_share <- whole_emi_elec %>% 
  mutate(share=value/whole_emi$value) %>% 
  filter(period<=2050) 
whole_emi_elec_share$variable <- "Emissions|CO2|Energy|Supply|Electricity|Share"
whole_emi_elec_share$unit <- ""
whole_emi_elec_share$value <- whole_emi_elec_share$share
hist_emi_elec_share <- hist_emi_elec %>% 
  mutate(share=hist_emi_elec$Value/hist_emi$Value)
hist_emi_elec_share$Value <- hist_emi_elec_share$share

# Contribution of coal power plants to total electricity emissions
# Use Primary Energy as proxy 
whole_pe_fossil <- whole %>% filter(variable %in% c("Primary Energy|Coal|Electricity","Primary Energy|Gas|Electricity"))

# "Primary Energy|Coal|w/ CCS","Primary Energy|Coal|w/o CCS" ,"Primary Energy|Gas|w/ CCS"  , "Primary Energy|Gas|w/o CCS","Primary Energy|Oil|w/ CCS" , "Primary Energy|Oil|w/o CCS",
hist_pe_coal_elec <- hist_and_botmup %>% filter(Variable=="PE|Coal|Electricity (EJ/yr)",Year %in% c(2005,2010,2015),Region=="IND")
hist_pe_gas_elec <- hist_and_botmup %>% filter(Variable=="PE|Gas|Electricity (EJ/yr)",Year %in% c(2005,2010,2015),Region=="IND")

line_type_1(whole_emi_elec_share,hist_emi_elec_share,c(2005,2010))
line_type_2(whole_emi_elec_share,hist_emi_elec_share,c(2005,2010))
ggplot()+
  geom_line(data = whole_pe_fossil %>% filter(period<2050,variable=="Primary Energy|Coal|Electricity") , aes(x=period,y=value,group=interaction(model,scen_name),linetype=model_scope,color=model))+facet_grid(variable~scen_name)+
 labs(
    x = "Year",
    y = "Primary Energy (EJ/yr)")+ theme_bw()+
   annotate("point",x=c(2005,2010,2015),y=hist_pe_coal_elec$Value)

ggplot()+
  geom_line(data = whole_pe_fossil %>% filter(period<2050,variable=="Primary Energy|Gas|Electricity") , aes(x=period,y=value,group=interaction(model,scen_name),linetype=model_scope,color=model))+facet_grid(variable~scen_name)+
 labs(
    x = "Year",
    y = "Primary Energy (EJ/yr)")+ theme_bw()+
   annotate("point",x=c(2005,2010,2015),y=hist_pe_gas_elec$Value)

```

The top two figures show the share of emissions from the electricity sector compared to the total emissions. The message here is similar to the last two figures. That both national and global models show power sector decarbonisation potential (compare here with other sectors), has already been mentioned above.
Decarbonisation of the electricity sector can take place in a multitude of ways - coal plants be retired, new coal plants are CCS enabled, and simply moving to renewable energy, i.e., Hydro, solar, wind, and nucler. The question is what is behind the emissions in the electricity sector in 2050. Taking Primary energy as a proxy for emissions by type of fuel, for early and delayed action, the plot is shown at the bottom. Out of the two national models from India in the modeling excercise, AIM/Enduse 3.0 and India Markal, only the former has CCS available as an option. Both national models show a resurgence of coal at some later part of time. For AIM/Enduse 3.0 this might be because of Coal CCS, but it is still unclear for _Markal_. In general, an early mitigation policy has almost no effect on coal output to power plants (see early action), but strangely PE decreases in 2030 before resurging again in 2035. For a delayed action, the dip in PE is small. Another interesting finding is that although the both models have comparable CO2 emissions from the electricity sector till 2020, their PE are quite different (maybe due to efficiency of plants?). For the global models, the pattern seems to be robust in delay scenarios, most project zero PE in 2050; meaning that the potential for coal CCS till is very limited. The pictures get hazy in the early action scenario for the time period between 2020 and 2050, with a wide range in the rates of decarbonisation and many having apparently coal CCS in the mix or coal w/o CCS and BECCS (but then again will BECCS become economically favourable before coal CCS?). Why does REMIND has such high PE Coal Elec values in 2030 and before? Why do almost all global models have much higher PE than national models? Should we convert PE Coal to tonnes of coal mined and see with current numbers? 
The picture for gas seems to be quite polar. India has much more coal than gas resources, and the push for clean cooking and vehicles/public transport using compressed natural gas, means that gas based electricity is expensive. The question is will India see transition from coal to gas based power, commonly seen in European nations? The two national models have completely divergent views on the same, including the global models.
This might be due to Coal CCS 
This might be the reason for the resurgence of coal in both the early and delay scenarios, albeit in a lower amount in the early action, due to early mitigation. The second model, India Markal 
In both the early and delayed scenarios, the national models show 

#### Share of emissions- Non-electricity sector
```{r}

```


#### Secondary and Final Energy of Electricity (model scope and technology)
```{r SE_Electricity,warning=FALSE,fig.show='hold',out.width="50%"}
# Secondary Energy of Electricity
plotvar_1 <- grep("Secondary Energy|Electricity|",unique(whole$variable),value=T,fixed = T)
whole_se_elec <-whole %>% filter(variable %in% plotvar_1 )
## adding all SE techs
whole_se_elec_sum <- whole_se_elec %>% 
  group_by(model,scenario,scen_name,period,model_scope,unit,modscen,unit) %>% 
  summarise(value=sum(value)) %>% 
  mutate(variable="Secondary Energy|Electricity")

# Historical SE
hist_se_elec <- hist_and_botmup %>% filter(Region=="IND", Year %in% c(2005,2010), Variable %in% grep("SE|Electricity",unique(hist_and_botmup$Variable),value=T,fixed = T))
hist_se_elec_sum <- hist_se_elec %>% 
  group_by(Region,Year) %>% 
  summarise(Value=sum(Value))

# FE
whole_fe_elec <- whole %>% filter(variable=="Final Energy|Electricity")
# Historical FE
hist_fe_elec <- hist_and_botmup %>% filter(Region=="IND", Year %in% c(2005,2010),Variable =="FE|Electricity (EJ/yr)") 

source("plotstyle.R")

line_type_1(whole_se_elec_sum,hist_se_elec_sum,c(2005,2010))
line_type_2(whole_se_elec_sum,hist_se_elec_sum,c(2005,2010))
line_type_1(whole_fe_elec,hist_fe_elec,c(2005,2010))
line_type_2(whole_fe_elec,hist_fe_elec,c(2005,2010))

ggplot()+
  geom_bar(data=whole_se_elec %>% filter(period==2030) , aes(x=scen_name,y=value,group=variable,fill=variable),position = "stack",stat = "identity")+scale_fill_manual(values=plotstyle(plotvar_1))+
  facet_grid(~model)+
    theme(strip.text.x = element_text(angle = 90,size = 8),axis.text.x = element_text(angle = 90, hjust = 1))+
  labs(
    x="Scenario",
    y = "Secondary Energy (EJ/yr) in 2030")
# 
ggplot()+
  geom_bar(data=whole_se_elec %>% filter(period==2050) , aes(x=scen_name,y=value,group=variable,fill=variable),position = "stack",stat = "identity")+scale_fill_manual(values=plotstyle(plotvar_1))+
  facet_grid(~model)+
    theme(strip.text.x = element_text(angle = 90,size = 8),axis.text.x = element_text(angle = 90, hjust = 1))+
  labs(
    x="Scenario",
    y = "Secondary Energy (EJ/yr) in 2050")
```


#### Transmission losses
```{r Elec_Efficiency,warning=FALSE,fig.show='hold',out.width="50%"}
whole_fe_elec <- whole_fe_elec %>% 
  arrange(model,scenario)
whole_se_elec_sum <- whole_se_elec_sum %>% 
  arrange(model,scenario)

 whole_se_elec_eff <- transform(whole_se_elec_sum,efficiency=whole_fe_elec$value/whole_se_elec_sum$value) 
#names(whole_se_elec_eff)[8] <- "value"

hist_elec_eff <- transform(hist_se_elec_sum,efficiency=hist_fe_elec$Value/Value)
#names(hist_elec_eff)[4] <- "Value"

ggplot()+
  geom_line(data = whole_se_elec_eff , aes(x=period,y=efficiency,group=interaction(model,scen_name),linetype=scen_name,color=model_scope)) +
   labs(
    x = "Year" ,
    y = "Elec. Efficiency",
    color = "Model Scope",
    linetype = "Scenario Type"
  ) +
  theme_bw()+ 
  coord_cartesian(xlim = c(2005,2050))+
  annotate(geom = "point",x =c(2005,2010),y=hist_elec_eff$efficiency)

ggplot()+
  geom_line(data = whole_se_elec_eff %>% filter(model %in% c("India MARKAL","AIM/Enduse 3.0")), aes(x=period,y=efficiency,group=interaction(model,scen_name),linetype=scen_name,alpha=model)) +
geom_line(data = whole_se_elec_eff %>% filter(!model %in% c("India MARKAL","AIM/Enduse 3.0")), aes(x=period,y=efficiency,group=interaction(model,scen_name),color=model,linetype=scen_name))+
    labs(
    x = "Year" ,
    y = "Elec. Efficiency",
    color = "Global Model",
    alpha="National Model",
    linetype = "Scenario Type")+
  theme_bw()+
  coord_cartesian(xlim = c(2005,2050))+
  annotate(geom = "point",x =c(2005,2010),y=hist_elec_eff$efficiency)

# line_type_1(whole_se_elec_eff,hist_elec_eff,c(2005,2010))
# line_type_2(whole_se_elec_eff,hist_elec_eff,c(2005,2010))
# #hist_fe <- hist_and_botmup %>% filter(Region=="IND", Year %in% c(2005,2010),Variable =="FE|Electricity (EJ/yr)") 
# ggplot(whole_fe %>% filter(scen_name=="Early action" & period<2050))+
#   geom_line(aes(x = period,y = value,color=model_scope,linetype=model)) +
#   facet_grid(~variable)

# line_type_1(whole_fe,hist_fe_elec,c(2005,2010))
# line_type_2(whole_fe,hist_fe_elec,c(2005,2010))
#### Coal capacity, generation and  
```

#### Primary and Secondary Energy of coal plants
```{r coal_plant_eff,warning=FALSE,fig.show='hold',out.width="50%"}
## Efficiency of coal plants


whole_pe_coal_elec <- whole %>%
                  filter(variable=="Primary Energy|Coal|Electricity")%>% 
                  arrange(model,scenario)
whole_se_coal_elec <- whole %>% 
                      filter(variable %in% c("Secondary Energy|Electricity|Coal|w/o CCS","Capacity|Electricity|Coal|w/ CCS"), model!="COPPE-COFFEE 1.0") %>%
                      arrange(model,scenario)

whole_se_coal_elec_eff <- transform(whole_se_coal_elec,efficiency=whole_se_coal_elec$value/whole_pe_coal_elec$value) 

# Coal capacity
whole_coal_cap <- whole %>% filter(variable %in% c("Capacity|Electricity|Coal|w/o CCS","Capacity|Electricity|Coal|w/ CCS")) %>% group_by(region,unit,period,modscen,model_scope,scenario,model_scope) %>% 
  summarise(value=sum(value)) %>% 
  mutate(variable="Capacity|Electricity|Coal")

  
# hist_coal_cap <- hist_and_botmup%>%
#   filter(grepl("Operating|Constr|Announced",Variable),Region=="IND")
# Current Capacity
hist_coal_cap <- hist_and_botmup%>% filter(Region=="IND", Variable =="Operating")
  hist_coal_cap$Value <- hist_coal_cap$Value/1000

  # line_type_1(whole_coal_cap,hist_coal_cap,2018)
  # line_type_2(whole_coal_cap,hist_coal_cap,2018)
  ggplot()+
  geom_line(data = whole_se_coal_elec_eff , aes(x=period,y=efficiency,group=interaction(model,scen_name),linetype=scen_name,color=model_scope)) +
   labs(
    x = "Year" ,
    y = "Plant efficiency",
    color = "Model Scope",
    linetype = "Scenario Type"
  ) +
  theme_bw()+ 
  coord_cartesian(xlim = c(2005,2050))
```
  
  
  
#### Cumulative Emissions 2011-2050
```{r cum_emi,warning=FALSE}
whole_cum <- whole_emi %>% 
  filter(period>2010 & period<2055) %>% 
  group_by(model,scen_name) %>% 
  mutate(cumsum=cumsum(value)/1000) %>% 
  arrange(cumsum,desc(cumsum))


# try 1
ggplot()+
  geom_bar(data=whole_cum %>% filter(period==2050) , aes(x=reorder(model,cumsum),y=cumsum, group=interaction(model,scen_name),fill=scen_name),position="dodge", stat = "identity")+
  labs(
    x = "Model name" ,
    y = "Cumulative Emissions of India (2011-2050) (Gt/yr)",
    fill = "Scenario Type",
    alpha = "Model Scope"
 
  ) +
  # theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  
  #scale_alpha_discrete(range = c(0.95, 0.55))
  facet_grid(~model_scope,scales="free",space = "free_x")


```

#### Capital Cost of Solar PV
```{r capital cost,message=FALSE,warning=FALSE,error=FALSE,purl=FALSE}
#plot capital cost
plotvar <- c("Capital Cost|Electricity|Solar|PV")
whole_cap_cost <- whole[whole$variable==plotvar,]
localrate = 0.015 #https://www.xe.com/currencycharts/?from=INR&to=USD&view=10Y
whole_cap_cost[whole_cap_cost$model %in% c("India MARKAL","AIM/Enduse 3.0"),]$value <- whole_cap_cost[whole_cap_cost$model %in% c("India MARKAL","AIM/Enduse 3.0"),]$value*localrate
proj_iea <- hist_and_botmup %>% filter(Region=="IND", Year %in% seq(2015,2040,5),Variable =="spv",Source=="IEA_WEO") 

line_type_1(whole_cap_cost,proj_iea,seq(2015,2040,5))
line_type_2(whole_cap_cost,proj_iea,seq(2015,2040,5))
```
? historical PV costs




#### Total Demand and Demand in various sectors
```{r FE, include=FALSE}
plotvar <- c("Final Energy","Final Energy|Industry","Final Energy|Residential and Commercial","Final Energy|Transportation","Final Energy|Other","Final Energy|Other Sector")
whole_fe <- whole[whole$variable %in% plotvar,]
```

```{r}
#Power generation in 2030
# all technologies
plotvar <- grep("Secondary Energy|Electricity|",unique(whole$variable),value=T,fixed = T)
whole_se_elec <- whole %>% filter(variable %in% plotvar )
whole_se_elec_tot <- whole %>% filter(variable== "Secondary Energy|Electricity")
source("plotstyle.R")

ggplot()+
  geom_bar(data=whole_se_elec %>% filter(period==2030) , aes(x=scen_name,y=value,group=variable,fill=variable),position = "stack",stat = "identity")+scale_fill_manual(values=plotstyle(plotvar))+
  facet_grid(~model)+
    theme(strip.text.x = element_text(angle = 90,size = 8),axis.text.x = element_text(angle = 90, hjust = 1))

ggplot()+
  geom_bar(data=whole_se_elec %>% filter(period==2050) , aes(x=scen_name,y=value,group=variable,fill=variable),position = "stack",stat = "identity")+scale_fill_manual(values=plotstyle(plotvar))+
  facet_grid(~model)+
    theme(strip.text.x = element_text(angle = 90,size = 8),axis.text.x = element_text(angle = 90, hjust = 1))  

# ggplot()+
#   geom_bar(data=whole_se_elec , aes(x=scen_name,y=value,group=variable,fill=variable),position = "stack",stat = "identity")+scale_fill_manual(values=plotstyle(plotvar))+
#   facet_grid(~model)+theme(strip.text = element_text(size=8,angle = 90))
   
# ggplot()+
#   geom_col(data=whole_se_elec,aes(x=modscen,y=value,group=interaction(model,variable),fill=variable)) + coord_flip()

  # scale_fill_manual(values=plotstyle(plotvar)) + xlab("Model - Scenario") +
  # geom_text(data=whole_se_elec,aes(x=model,y=25,label=model_scope,angle=90,hjust="right"),color="red",size=2.5)+
  # geom_point(data=whole_se_elec_tot,aes(x=modscen,y=value))+ylim(0,25)+
  # theme_bw()+ylab("Secondary Energy Electricity in 2030 (EJ/yr)")

```
#### Capacity Factor
The capacity factor of a plant is defined as the fraction of time it is available in a year for electricity generation.$$  $$

```{r}
# removing observations in whole_se_coal that are not in whole_cap_coal
 
# whole_se_coal <- whole %>% 
#   filter(!modscen %in% c("COPPE-COFFEE 1.0 - NPi2020_1000_V3","AIM/Enduse 3.0 - INDC2030_low_V3","COPPE-COFFEE 1.0 - INDC2030i_1000_V3")) %>% 
#   mutate(cap_factor=value*277777.778/(whole_coal_cap$value*8760)) %>%   
#   mutate(capacity=whole_coal_cap$value) %>% 
#   filter(capacity!=0)
#                         
# ggplot()+
#   geom_line(data = whole_se_coal, aes(x=period,y=cap_factor,group=interaction(model,scen_name),linetype=scen_name,color=model_scope)) +
#    labs(
#     x = "Year" ,
#     y = "Capacity Factor",
#     color = "Model Scope",
#     linetype = "Scenario Type"
#   ) +
#   theme_bw()+ 
#   coord_cartesian(xlim = c(2005,2050))

```




```{r}
head(hist_and_botmup%>%
  filter(grepl("Operating|Constr|Announced",Variable),Region=="IND"))
```

# Power capacity in 2030
```{r power_cap}
#Power capacity in 2030
source("plotstyle.R")
plotvar <- grep("Capacity|Electricity|",unique(whole$variable),value=T,fixed = T)
plotvar <- plotvar[-c(13,14)]#removing Solar|PV and Wind|Onshore


whole_cap_elec <- whole[whole$variable %in% plotvar & whole$period==2030,]
coal <- hist_and_botmup%>%
  filter(grepl("Operating|Constr|Announced",Variable),Region=="IND")
whole_j <- whole[whole$period==2030 & whole$variable %in% "Capacity|Electricity|Solar|PV" & whole$model %in% c("AIM V2.1","AIM/CGE","DNE21+ V.14", "REMIND-MAgPIE 1.7-3.0"),]
# whole_j <- whole[whole$period==2030 & whole$variable %in% "Capacity|Electricity|Solar|PV" ,]
# whole_j_2 <-  whole[whole$period==2030 & whole$variable %in% "Capacity|Electricity|Solar" ,]
#what <- grep("Wind",unique(whole$variable),value=T)
whole_j$variable <- "Capacity|Electricity|Solar"

whole_cap_elec <- rbind(whole_cap_elec,whole_j)

whole_cap_elec_tot <- whole[whole$period==2030 & whole$variable %in% "Capacity|Electricity" ,]


ggplot()+
  geom_bar(data=whole_cap_elec , aes(x=reorder(scen_name,value),y=value,group=variable,fill=variable),position = "stack",stat = "identity")+scale_fill_manual(values=plotstyle(plotvar))+
  facet_grid(~model)
  


# ggplot()+
#   geom_bar(data=whole_cap_elec %>% filter(scen_name=="Early action"), aes(x=reorder(model,value),y=value,group=interaction(model,modscen),fill=variable),position = "dodge")+coord_flip()+scale_fill_manual(values=plotstyle(plotvar))

```


```{r}
ggplot()+
  geom_col(data=whole_cap_elec,aes(x=model,y=value,group=interaction(scen_name,variable,model),fill=variable))+
  scale_fill_manual(values=plotstyle(plotvar))+
  xlab("Model - Scenario")+
  geom_text(data=whole_cap_elec,aes(x=model,y=1200,label=scen_name,hjust="right"),color="red",size=2.5)+coord_flip()+
  ylim(0,1300)+ theme_bw()+ylab("Power Capacity (GW)")+ 
# geom_point(data=whole_l,aes(x=modscen,y=value))
ggsave(file="Capacity_IND.png",width=8,height=5)
```
#### Share of Electricity to total CO2 Emissions  
```{r,message=FALSE,warning=FALSE,error=FALSE,purl=FALSE}
# Share of Electricity to total CO2 Emissions
whole_emi_elec_share <- whole_emi_elec %>% 
  mutate(share=value/whole_emi$value) %>% 
  filter(period<=2050) 
whole_emi_elec_share$variable <- "Emissions|CO2|Energy|Supply|Electricity|Share"
whole_emi_elec_share$unit <- ""
whole_emi_elec_share$value <- whole_emi_elec_share$share
hist_emi_elec_share <- hist_emi_elec %>% 
  mutate(share=hist_emi_elec$Value/hist_emi$Value)
hist_emi_elec_share$Value <- hist_emi_elec_share$share
line_type_1(whole_emi_elec_share,hist_emi_elec_share,c(2005,2010))
line_type_2(whole_emi_elec_share,hist_emi_elec_share,c(2005,2010))

# ggplot()+
#   geom_bar(data=whole_emi_elec_share %>% filter(period==2010),aes(x=reorder(model,share),y=share, group=interaction(model,scen_name),fill=scen_name,alpha=model_scope),position="dodge", stat = "identity")+coord_flip()+
#   scale_alpha_discrete(range = c(0.95, 0.65))+
#   labs(
#     x = "Year" ,
#     y = "CO2 Emissions Electricity (Gt/yr)")

```
#### Final Energy of Electricity
```{r FE_Electricity,message=FALSE,warning=FALSE,error=FALSE,purl=FALSE}
plotvar <- "Final Energy|Electricity"
whole_fe_elec <- whole[whole$variable==plotvar,]
hist_fe_elec <- hist_and_botmup %>% filter(Region=="IND", Year %in% c(2005,2010),Variable =="FE|Electricity (EJ/yr)") 

line_type_1(whole_fe_elec,hist_fe_elec,c(2005,2010))
line_type_2(whole_fe_elec,hist_fe_elec,c(2005,2010))
```

#### Secondary Energy of Electricity
#```{r SE_Electricity,message=FALSE,warning=FALSE,error=FALSE,purl=FALSE}
# all tech with secondary energy of electricity
plotvar <- grep("Secondary Energy|Electricity|",unique(whole$variable),value=T,fixed = T)
whole_se_elec <-whole[whole$variable %in% plotvar,]
## adding all SE techs
whole_se_elec_sum <- whole_se_elec %>% 
  group_by(model,scenario,scen_name,period,model_scope,unit) %>% 
  mutate(value=sum(value))
whole_se_elec_sum$variable <- "Secondary Energy|Electricity"
# Sum over all variables to get secondary energy electricity
hist_se_elec <- hist_and_botmup %>% filter(Region=="IND", Year %in% c(2005,2010), Variable %in% grep("SE|Electricity",unique(hist_and_botmup$Variable),value=T,fixed = T))
hist_se_elec_sum <- hist_se_elec %>% 
  group_by(Region,Year) %>% 
  summarise(Value=sum(Value))

line_type_1(whole_se_elec_sum,hist_se_elec_sum,c(2005,2010))
line_type_2(whole_se_elec_sum,hist_se_elec_sum,c(2005,2010))
```

Global models have a 1000 Gt carbon budget (mitigation policy for 2C  between 2011-2100. They run the global models and get particular emission trajectories for India. These models minimise costs, so often developing nations, where mitigation is cheaper and most of the infrastructure has yet to be built get a disproportionate amount of the mitigation effort.  For the well-below 2 °C target, cumulative 2011−2100 net emissions are limited to 1000 Gt CO2, whereas the 1.5 °C scenario has a budget of 400 GtCO2. These budget values represent a likelihood of 66% of staying below 2 °C throughout the 21st century in the 'well below 2 °C' scenarios, as well as 66% of staying below 1.5 °C after 2100 in the 1.5 °C scenario

For the global models, the carbon budget for both the early and delay mitigation scenarios is the same, but till 2100 (and hence it cannot be seen till 2050). For them, the cumulative emissions in 2050 are higher. That the emissions rise without a cliamte policy in place is no surprise, but what is the cause of these rise in emissions?

The national budgets were decided after discussion with the global teams- The global teams gave them a number that they could work with?. 

? Recapitulate how the national budgets were calculated


Each of the two CO2 budget are achieved by iteratively adjusting a global carbon price that is assumed to grow with 5% p.a. until 2060 and linearly thereafter. Regionally fragmented carbon prices in 2020 (for the cost-effective scenarios) or 2030 (for the other scenarios) converge to the globally harmonized carbon price over a 20 year period (see figure S2 in the supplementary material). GHGs other than CO2 are priced equivalently to CO2 throughout the 21st century based on 100 year global warming potentials from IPCC's Fifth Assessment Report.

#### Secondary Energy from Coal 
```{r SE_Elec_Coal,include=FALSE}
whole_se_coal <- whole %>% filter(variable %in% c("Secondary Energy|Electricity|Coal|w/o CCS"))  
hist_se_coal <- hist_and_botmup %>% filter(Region=="IND", Year %in% c(2005,2010), Variable =="SE|Electricity|Coal (EJ/yr)")

line_type_1(whole_se_coal,hist_se_coal,c(2005,2010))
line_type_2(whole_se_coal,hist_se_coal,c(2005,2010))

```

